Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-29 paper/main.tex
Updated and rearranged

\section{Model}
\label{sec:model}
We define here a hierarchically supervised LDA model.  We assume a pre-specified set of labels $\mathcal{L}$. Each document is assigned a response of either -1 or 1 for at least one, but potentially many, label(s) in $\mathcal{L}$.  A response of 1 or -1 to label $l$ indicates if the document respectively is or is not $l$.  The label $l$ for a document $d$ will be used interchangeably to refer the observed response of document $d$ to label $l$. The label set is assumed to be an ``is a" hieararchy.  This means that if a label $l_1$ is a parent of label $l_2$ in the hierarchy and document $d$ has a positive response to the label $l_2$ then document $d$ also has a positive response to the label $l_1$.  Seen in a negative light, if document $d$ has a negative response to the $l_1$ label then document $d$ also has a negative response to the $l_2$ label.  To capture this hierarchical structure we model the labeling of documents using a generative cascade of conditional probit regression models.  Approximate inference is performed using Gibbs sampling.

% generalize to arbitrary codes (not just ICD-9's
%
%
\begin{figure}[h]
%tbp] %  figure placement: here, top, bottom, or page
 \centering \includegraphics[scale=0.3]{Graphical_Model2} \caption{adapted sLDA model}
\label{fig:example} 
\end{figure}
%
The fixed parameters of the model are the number of topics $K$, the number of unique words in the vocabulary $V$, the number of documents $D$, and the standard deviation $\sigma$ used in a normal prior distribution.  The hyper-parameters $\alpha^\prime$, $\alpha$, and $\gamma$ are weight parameters for Dirichlet prior distributions. We will denote the $K$-dimensional Dirichlet distribution as Dir$_K(\cdot)$ and the $K$ dimensional normal distribution as $\mathcal{N}_k(\cdot)$.

We will now describe the stochastic generative process which defines our model.  The graphical model is show in Figure~\ref{fig:example}. 
%
%Given the number of topics, K, and broad gamma priors on hyperparameters,
%the generative process is as follows: 
\begin{enumerate}
	\item For each topic $k = 1,\ldots, K$:
	\begin{itemize}
		\item Draw a distribution over words $\mathbf{\phi_{k}}\sim {\rm Dir}_{V}\left(\gamma \mathbf{1}\right)$, where $\mathbf{1}$ is a vector of ones of length $V$
	\end{itemize}

	\item For each label $l \in \mathcal{L}$:
	\begin{itemize}
		\item Draw the regression coefficients $\mathbf{\eta_l} \ | \ \sigma \sim \mathcal{N}_{K} \left( -\mathbf{1}, \sigma I_K \right)$, where $I_K$ is the $K$ dimensional identity matrix
	\end{itemize}

	\item Draw a prior over topic proportions $\mathbf{\beta}\mid\alpha'\sim {\rm Dir}_{K} \left(\alpha^{\prime} \mathbf{1} \right)$

	\item For each document $d = 1, \ldots, D$:
	\begin{itemize} 
		\item Draw topic proportions $\mathbf{\theta_{d}} \ | \ \mathbf{\beta},\alpha \sim {\rm Dir}_{K}\left(\alpha \mathbf{\beta} \right)$ 
		\item For $n = 1, \ldots, N_d$:
		\begin{itemize}
			\item Draw topic assignment $z_{n,d} \ | \ \mathbf{\theta_{d}} \sim {\rm Multinomial} \left(\mathbf{\theta_{d}} \right)$ 
			\item Draw word $w_{n,d} \ | \ z_{n,d},\mathbf{\beta_{1:K}} \sim {\rm Multinomial} \left(\mathbf{\beta_{z_{n,d}}} \right)$ 
		\end{itemize}

		\item For each label $l \in \mathcal{L}$:
		\begin{itemize}
			\item Draw $a_{l,d}\mid z_{1:N_{d},d},\eta_{l},y_{parent(l),d}\sim\begin{cases}
				\mathcal{N}\left(\bar{z}^{T}\eta_{l},1\right), & y_{parent(l)}=1\\
				\mathcal{N}\left(\bar{z}^{T}\eta_{l},1\right)I\left(a_{l,d}<0\right), & y_{parent(l)}=-1\end{cases}$ where $\bar{z_{d}}=N_{d}^{-1}\sum_{n=1}^{N}z_{n,d}$ 
			%\item Draw $a_{l, d} \ | \ z_{1:N_d,d}, \eta_l \sim \mathcal{N} \left(\bar z_d^{T} \eta_{l},1\right)$, where $\bar z_d=N_d^{-1}\sum_{n=1}^{N_d}z_{n,d}$ 
			\item Set the response variable \begin{equation*} y_{l, d} \ | \ a_{l, d} = \begin{cases}
																										 \ \ \ 1 & \text{if $a_{l,d} > 0$ and $y_{{\rm parent}(l),d} = 1$} \\
																										-1 & \text{otherwise}
																								\end{cases}  
															 \end{equation*}															 
		\end{itemize}
	\end{itemize}
\end{enumerate}
%
This type of generative model is known as a probit regression model. Probit regression is like logistic regression except instead of modeling the logit of $P(y = 1)$ using a linear form we model $\Phi^{-1}(P(y = 1))$ using a linear form, where $\Phi(\cdot)$ is the CDF for a standard normal distribution.  In this case, the regression is conditional on the parents according to the constraints of the labeling hierarchy. The latent variables $a_{l,d}$ utilized here are also known as an auxiliary variables because the are introduced to make exact Gibbs sampling possible and are not of primary interest.  
%
\section{Inference}
\label{sec:inference}
%
In the Bayesian approach to statistical modeling the primary task of inference is to find the posterior distribution over the unobserved parameters of the model. However, it will often be the case that the set of labels $\mathcal{L}$ is not fully observed for every document.  We will define $\mathcal{L}_d$ to be the subset of labels which have been observed for document $d$.  It is straightforward to integrate out the variables $a_{l^\prime,d}$ and $y_{l^\prime,d}$ for $l^\prime \in \mathcal{L} \backslash \mathcal{L}_d$ from the full generative model.  We can also integrate out the parameters $\mathbf{\phi_{1:K}}$ and $\mathbf{\theta_{1:D}}$ as in \citet{Griffiths04}.  Therefore, in our model the latent variables are $\mathbf{z} = \{ z_{1:N_d,d} \}_{d = 1, \ldots, D},\mathbf{\eta} = \{ \mathbf{\eta_l} \}_{l \in \mathcal{L}},\mathbf{a} = \{ a_{l,d}\}_{l \in \mathcal{L}, d = 1, \ldots, D}, \mathbf{\beta}, \alpha, \alpha^{\prime}$ and $\gamma$.

The posterior distribution we seek cannot be solved in closed form. This is often the case in evaluating posterior distributions of non-trivial probabilistic models. We will appeal to one of the common methods for approximating posterior distributions in the face of intractable normalization factors: Markov chain Monte Carlo (MCMC) sampling. Since in this model it is possible to sample from the conditional distributions for all variables we will use the Gibbs sampling algorithm to obtain an approximation to this posterior. In particular, we will derive a collapsed Gibbs sampler.
%
%
%Given an observation of a set of observed labels and a document, the posterior distribution for the latent variables is
%
%\begin{equation}
%p\left(\theta,z_{1:N},\phi_{1:K},\eta_{i_{l,c}\in\mathcal{I}},a_{i_{l,c}\in\mathcal{I}},\beta,\alpha,\alpha',\gamma\mid w_{1:N},y_{i_{l,c}\in\mathcal{I}};\sigma,\lambda\right)\label{eq:Posterior}\end{equation}
%\[
%=\frac{p\left(\theta,z_{1:N},\phi_{1:K},\eta_{i_{l,c}\in\mathcal{I}},a_{i_{l,c}\in\mathcal{I}},\beta,\alpha,\alpha',\gamma,w_{1:N},y_{i_{l,c}\in\mathcal{I}};\sigma,\lambda\right)}{\int_{\theta,\phi,a,\eta,\alpha,\alpha',\beta,\gamma}\sum_{z}p\left(\theta,z_{1:N},\phi_{1:K},\eta_{i_{l,c}\in\mathcal{I}},a_{i_{l,c}\in\mathcal{I}},\beta,\alpha,\alpha',\gamma,w_{1:N},y_{i_{l,c}\in\mathcal{I}};\sigma,\lambda\right)}\]
%
\subsection{Gibbs Sampler}

We derive a collapsed Gibbs sampler for this model by considering the individual conditional probability distributions for
each of the unobserved variables.  We use the notation $\mathbf{z}_{-(n,d)}$ to denote $\mathbf{z} \backslash z_{n,d}$.
%, marginalizing
%$\theta_{1:D}$ and $\phi_{1:K}$. For details regarding collapsing
%in LDA models see \citet{Griffiths04}. 
\subsubsection{$p\left(z_{n,d} \mid\mathbf{z_{-\left(n,d\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)$}
%
First we consider the conditional distribution of the assignment variable for each word $n = 1, \ldots, N_d$ in documents $d = 1, \ldots, D$.  The conditional distribution does not include $\theta_{1:D}$ and $\phi_{1:K}$ because they have been integrated out as in the collapsed Gibbs sampler \citep{Griffiths04}.  The conditional distribution of $z_{n,d}$ is proportional to the joint distribution of its markov blanket, explicitly this means
%\begin{equation}
%p\left(z_{d,n}\mid\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)\propto p\left(z_{d,n},\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)\end{equation}
%
%
%Due to the factorization of this model, we can rewrite the joint distribution
%as the following:
%
\begin{equation}
p\left(z_{n,d}\mid\mathbf{z_{-\left(n,d\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)\propto \prod_{l \in \mathcal{L}_d}p\left(a_{l,d}\mid\mathbf{z},\eta_l \right)p\left(z_{n,d} \ | \ \mathbf{z_{-\left(n, d \right)}},\mathbf{a},\mathbf{w},\alpha,\beta,\gamma\right).
\end{equation}
%
The product is only over the subset of labels $\mathcal{L}_d$ which have been observed for document $d$. By isolating terms that depend on $z_{n,d}$ and absorbing all other terms into a normalizing constant \citep{Griffiths04} we find 
%
\begin{eqnarray}
\lefteqn{p\left(z_{n,d} = k \mid\mathbf{z_{-\left(n,d\right)}},\mathbf{a},\mathbf{w}, \mathbf{\eta},\alpha,\beta,\gamma\right)\propto} \nonumber\\ 
& \hspace{2cm}  \left(n_{\left(\cdot\right),d}^{k,-\left(n,d\right)}+\alpha\beta_{k}\right)\frac{n_{w_{n,d},\left(\cdot\right)}^{k,-\left(n,d\right)}+\gamma}{\left(n_{\left(\cdot\right),\left(\cdot\right)}^{k,-\left(n,d\right)}+V\gamma\right)} \prod_{l \in \mathcal{L}_d} \exp\left\{ -\frac{\left(\bar z_d^{T}\eta_{l}-a_{l,d} \right)^{2}}{2}\right\}\label{eq:z-likelihood}.
\end{eqnarray}
%
Here, $n_{v,d}^{k,-\left(n, d^{\prime} \right)}$ represents the number of words of type $v$ in document $d$ assigned to topic $k$ omitting the $n^{\rm th}$ word of document $d^{\prime}$.  The notation $(\cdot)$ in the subscript means the count resulting from summing over the omitted subscript variable.  Given Equation \ref{eq:z-likelihood}, $p\left(z_{d,n}\mid\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\mathbf{\beta},\gamma\right)$ can be sampled through enumeration.
%
\subsubsection{$p\left(\mathbf{\eta_l}\mid\mathbf{z},\mathbf{a},\sigma\right)$}
%
We now consider the conditional distribution of the regression coefficients $\mathbf{eta_l}$ for $l \in \mathcal{L}$.  Given that $\mathbf{\eta_l}$ and $a_{l,d}$ are distributed normally, the posterior distribution of $\mathbf{\eta_l}$ is normally distributed with mean $\hat \mu$ and covariance $\hat{\mathbf{\Sigma}}$ such that
% (probably not the right place for this) We evaluated the model over various values of $\sigma$ where $\sigma=\left\{ 0.01,0.1,0.25,1,2\right\} $.
\begin{eqnarray}
\hat{\mathbf{\Sigma}}^{-1} &=&\mathbf{I}\sigma^{-1}+\bar{\mathbf{Z}}^{T}\bar{\mathbf{Z}} \\
\hat \mu &=&\hat{\mathbf{\Sigma}}_{i}\left(-\mathbf{1}\sigma^{-1}+\bar{\mathbf{Z}}^{T}\mathbf{a}_l\right). 
\end{eqnarray}
This is a standard result from normal Bayesian linear regression \citep{BishopPRML}.  Here, $\bar{\mathbf{Z}}$ is a $D \times K$ matrix such that row $d$ of $\mathbf{\bar Z}$ is $\bar z_d$, and $\mathbf{a}_l = [a_{l,1}, a_{l,2}, \ldots, a_{l,D}]^T$.
%
%
%
%p\left(\eta_{i_{l,c}}\mid\mathbf{z}_{1:D},\mathbf{a};\sigma\right)=\mathcal{N}\left(\eta_{i_{l,c}}\mid\hat{\mu}_{i},\hat{\Sigma}_{i}\right)\end{equation}
%
%\[
%
%
%
%\[

@@

In the section we describe the application of HSLDA for prediction
in two hierarchically structured domains. Firstly, we describe using
discharge summaries to predict diagnoses, encoded as ICD-9 codes.
Discharge summaries are documents that are authored by clinicians
to summarize the course of someone who has been hospitalized. ICD-9
codes are used mainly for billing purposes to indicate the conditions
for which a patient was treated. Secondly, we describe using Amazon.com
product descriptions to predict product categories.

\subsection{Diagnosis Prediction}

@@

For each hospitalization there are usually several ICD-9 codes assigned
for billing purposes. These codes are known to be quite specific but
not very sensitive {[}citation{]}. Regardless of that fact, this is
one of the only sources for information on patient diagnoses aside
from the free text. Aside from prediction, one of the goals is to
compare the sensitivity of predictions from the HSLDA model in comparison
to the codes in a case where a test closer to ground truth is available.
For this we will compare whether predictions for the ICD-9 code associated
with anemia are better predicted by HSLDA or by the ICD-9 codes. Anemia
was chosen because hemoglobin values are readily available and the
definition of anemia according the World Health Organization is approximately
12.5, with a threshold of 12 for women and 13 for men {[}citation{]}.

@@

\subsection{Product Category Prediction}

Data for these experiments were obtained partially from the Stanford
Network Analysis Platform (SNAP) Amazon product metadata dataset and
partially directly from the the Amazon.com website. The product ID's
and categorizations were obtained from the SNAP dataset and the product
descriptions were obtained directly from the website.

@@

\subsection{Evaluation}

The two main methods of evaluation for the model are prediction and
topic quality. We compare model performance against 3 similar models
to demonstrate that each component of the model is important for performance.
Specifically, we evaluate models including independent regressors
+ sLDA (hierarchical constraints on labels ignored), HSLDA fit by
running LDA first then running tree-conditional regressions, and HSLDA
fit with fixed random regression parameters.

@@

There have been many models that incorporate both latent models of
text and some form of supervision {[}citations{]}. One set of models
that are particularly relevant to HSLDA are Chang and Blei's {[}citation{]}
hierarchical models for document networks. In that family of models,
they encountered a similar scenario where the lack of a link did not
truly indicate absence. In our model, the lack of a code in the hierarchy
being assigned does not necessarily indicate absence. Therefore, as
in the work of Chang and Blei, we employ regularization in the form
of a negative prior on the regression parameters to provide a prior
that indicates a bias towards being truly negative in the absence
of a code.

>>>>

There have been many models that incorporate both latent models of
text and some form of supervision \citep{Ramage2009,DiscLDA,wangbleifeifei08,RelationalLDA}.
One set of models that are particularly relevant to HSLDA are Chang
and Blei's hierarchical models for document networks (Relational Topic
Models). In that family of models, they encountered a similar scenario
where the lack of a link did not truly indicate absence. In hierarchically
labeled data, negative labels are uncommon and the lack of a label
in the hierarchy is not equivalent to a negative label. Therefore,
as in the work of Chang and Blei, we employ regularization to account
for the lack of negative labels. This will be discussed further in
\ref{sec:model}.

\section{Model}

\label{sec:model} We define here a hierarchically supervised LDA
model. Although we will focus on document modeling in our description
and experiments, this model applies equally well to other collections
of discrete data with hierarchically constrained labels.

We assume a pre-specified set of labels $\mathcal{L}=\left\{ l_{1},l_{2},\ldots,l_{\left|\mathcal{L}\right|}\right\} $.
Each document is assigned a response of either -1 or 1 for at least
one, but potentially many labels in $\mathcal{L}$. The label, $l$,
for a document, $d$, will be used interchangeably to refer to the
observed response of document $d$ to label $l$. The label set is
assumed to be structured as an {}``is-a'' hieararchy.
To understand this, consider a hierarchy where label $l_{1}$ is a
parent of label $l_{2}$. If document $d$ has a positive response
to label $l_{2}$ then it will also have a positive response to label
$l_{1}$. Conversely, if document $d$ has a negative response to
label $l_{1}$ then it will also has a negative response to $l_{2}$.
To capture this hierarchical structure we model the labeling of documents
using a generative cascade of conditional probit regression models.

% generalize to arbitrary codes (not just ICD-9's
%
\begin{figure}[h]
%tbp] %  figure placement: here, top, bottom, or page
 \centering \includegraphics[scale=0.3]{Graphical_Model2} \caption{adapted sLDA model}

\label{fig:example} 
\end{figure}

The fixed parameters of the model are the number of topics $K$, the
number of unique words in the vocabulary $V$, the number of documents
$D$, as well as the mean, $\mu$, and the standard deviation, $\sigma$,
used in a normal prior distribution. The hyper-parameters $\alpha^{\prime}$,
$\alpha$, and $\gamma$ are weight parameters for Dirichlet prior
distributions. We will denote the $K$-dimensional Dirichlet distribution
as Dir$_{K}(\cdot)$ and the $K$ dimensional normal distribution
as $\mathcal{N}_{K}(\cdot)$.

We will now describe the stochastic generative process which defines
our model. The graphical model is show in Figure~\ref{fig:example}.
%Given the number of topics, K, and broad gamma priors on hyperparameters,
%the generative process is as follows:

\begin{enumerate}
\item For each topic $k=1,\ldots,K$:

\begin{itemize}
\item Draw a distribution over words $\mathbf{\phi_{k}}\sim{\rm Dir}_{V}\left(\gamma\mathbf{1}\right)$,
where $\mathbf{1}$ is a vector of ones of length $V$ 
\end{itemize}
\item For each label $l\in\mathcal{L}$:

\begin{itemize}
\item Draw the regression coefficients $\mathbf{\eta_{l}}\mid\sigma\sim\mathcal{N}_{K}\left(\mu I_{K},\sigma I_{K}\right)$,
where $I_{K}$ is the $K$ dimensional identity matrix 
\end{itemize}
\item Draw a prior over topic proportions $\mathbf{\beta}\mid\alpha'\sim{\rm Dir}_{K}\left(\alpha^{\prime}\mathbf{1}\right)$
\item For each document $d=1,\ldots,D$:

\begin{itemize}
\item Draw topic proportions $\mathbf{\theta_{d}}\mid\beta,\alpha\sim{\rm Dir}_{K}\left(\alpha\mathbf{\beta}\right)$ 
\item For $n=1,\ldots,N_{d}$:

\begin{itemize}
\item Draw topic assignment $z_{n,d}\mid\mathbf{\theta_{d}}\sim{\rm Multinomial}\left(\mathbf{\theta_{d}}\right)$ 
\item Draw word $w_{n,d}\mid z_{n,d},\mathbf{\beta_{1:K}}\sim{\rm Multinomial}\left(\mathbf{\beta_{z_{n,d}}}\right)$ 
\end{itemize}
\item For each label $l\in\mathcal{L}$:

\begin{itemize}
\item Draw $a_{l,d}\mid z_{1:N_{d},d},\eta_{l},y_{parent(l),d}\sim\begin{cases}
\mathcal{N}\left(\bar{z}^{T}\eta_{l},1\right), & y_{parent(l)}=1\\
\mathcal{N}\left(\bar{z}^{T}\eta_{l},1\right)I\left(a_{l,d}<0\right), & y_{parent(l)}=-1\end{cases}$ where $\bar{z_{d}}=N_{d}^{-1}\sum_{n=1}^{N}z_{n,d}$ %\item Draw $a_{l, d} \ | \ z_{1:N_d,d}, \eta_l \sim \mathcal{N} \left(\bar z_d^{T} \eta_{l},1\right)$, where $\bar z_d=N_d^{-1}\sum_{n=1}^{N_d}z_{n,d}$

\item Set the response variable \[
y_{l,d}\mid a_{l,d}=\begin{cases}
\ \ \ 1 & \text{if \ensuremath{a_{l,d}>0}and \ensuremath{y_{{\rm parent}(l),d}=1}}\\
-1 & \text{otherwise}\end{cases}\]

\end{itemize}
\end{itemize}
\end{enumerate}
This type of generative model is known as a probit regression model.
Probit regression models are a type of discriminative probabilistic
model similar to logistic regression. However, instead of using the
logistic sigmoid as the link function, the probit regression model
uses the CDF for a standard normal distribution - the inverse of which
is known as the probit. In this case, the regression is conditional
on the parents according to the constraints of the labeling hierarchy.
The latent variables $a_{l,d}$ utilized here are also known as an
auxiliary variables because the are introduced to make exact Gibbs
sampling possible and are not of primary interest.

Given that negative labels are uncommon and that the absence of a
label is not equivalent to a negative label, we apply an informative
prior to the regression parameters, $\mathbf{\eta}_{\mathcal{L}}$,
in the form of a negative prior that encodes a bias towards being
truly negative in the absence of a label.

\section{Inference}

\label{sec:inference} In the Bayesian approach to statistical modeling,
the primary task of inference is to find the posterior distribution
over the unobserved parameters of the model. However, it is often
possible and desirable to integrate over certain variables in the
model, also known as collapsing. In our model, it will often be the
case that the set of labels $\mathcal{L}$ is not fully observed for
every document. We will define $\mathcal{L}_{d}$ to be the subset
of labels which have been observed for document $d$. It is straightforward
to integrate out the variables $a_{l^{\prime},d}$ and $y_{l^{\prime},d}$
for $l^{\prime}\in\mathcal{L}\backslash\mathcal{L}_{d}$ from the
full generative model. We can also integrate out the parameters $\mathbf{\phi_{1:K}}$
and $\mathbf{\theta_{1:D}}$ as in \citet{Griffiths04}. Therefore,
in our model the latent variables are $\mathbf{z}=\{z_{1:N_{d},d}\}_{d=1,\ldots,D},\mathbf{\eta}=\{\mathbf{\eta_{l}}\}_{l\in\mathcal{L}},\mathbf{a}=\{a_{l^{\prime},d}\}_{l^{\prime}\in\mathcal{L}_{d},d=1,\ldots,D},\mathbf{\beta},\alpha,\alpha^{\prime}$
and $\gamma$.

The posterior distribution we seek cannot be solved in closed form.
This is often the case in evaluating posterior distributions of non-trivial
probabilistic models. We will appeal to one of the common methods
for approximating posterior distributions in the face of intractable
normalization factors: Markov chain Monte Carlo (MCMC) sampling. Since
in this model it is possible to sample from the conditional distributions
for all variables we will use the Gibbs sampling algorithm to obtain
an approximation to this posterior. %In particular, we will derive a collapsed Gibbs sampler.
%Given an observation of a set of observed labels and a document, the posterior distribution for the latent variables is
%\begin{equation}
%p\left(\theta,z_{1:N},\phi_{1:K},\eta_{i_{l,c}\in\mathcal{I}},a_{i_{l,c}\in\mathcal{I}},\beta,\alpha,\alpha',\gamma\mid w_{1:N},y_{i_{l,c}\in\mathcal{I}};\sigma,\lambda\right)\label{eq:Posterior}\end{equation}
%\[
%=\frac{p\left(\theta,z_{1:N},\phi_{1:K},\eta_{i_{l,c}\in\mathcal{I}},a_{i_{l,c}\in\mathcal{I}},\beta,\alpha,\alpha',\gamma,w_{1:N},y_{i_{l,c}\in\mathcal{I}};\sigma,\lambda\right)}{\int_{\theta,\phi,a,\eta,\alpha,\alpha',\beta,\gamma}\sum_{z}p\left(\theta,z_{1:N},\phi_{1:K},\eta_{i_{l,c}\in\mathcal{I}},a_{i_{l,c}\in\mathcal{I}},\beta,\alpha,\alpha',\gamma,w_{1:N},y_{i_{l,c}\in\mathcal{I}};\sigma,\lambda\right)}\]

\subsection{Gibbs Sampler}

We derive a collapsed Gibbs sampler for this model by considering
the individual conditional probability distributions for each of the
unobserved variables. We use the notation $\mathbf{z}_{-(n,d)}$ to
denote $\mathbf{z}\backslash z_{n,d}$. %, marginalizing
%$\theta_{1:D}$ and $\phi_{1:K}$. For details regarding collapsing
%in LDA models see \citet{Griffiths04}.

\subsubsection{$p\left(z_{n,d}\mid\mathbf{z_{-\left(n,d\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)$}

First we consider the conditional distribution of the assignment variable
for each word $n=1,\ldots,N_{d}$ in documents $d=1,\ldots,D$. The
conditional distribution does not include $\theta_{1:D}$ and $\phi_{1:K}$
because they have been integrated out as in the collapsed Gibbs sampler
\citep{Griffiths04}. The conditional distribution of $z_{n,d}$ is
proportional to the joint distribution of its markov blanket. %\begin{equation}
%p\left(z_{d,n}\mid\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)\propto p\left(z_{d,n},\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)\end{equation}
%Due to the factorization of this model, we can rewrite the joint distribution
%as the following:
\begin{equation}
p\left(z_{n,d}\mid\mathbf{z_{-\left(n,d\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)\propto\prod_{l\in\mathcal{L}_{d}}p\left(a_{l,d}\mid\mathbf{z},\eta_{l}\right)p\left(z_{n,d}\ |\ \mathbf{z_{-\left(n,d\right)}},\mathbf{a},\mathbf{w},\alpha,\beta,\gamma\right).\end{equation}
 The product is only over the subset of labels $\mathcal{L}_{d}$
which have been observed for document $d$. By isolating terms that
depend on $z_{n,d}$ and absorbing all other terms into a normalizing
constant as in \citep{Griffiths04} we find \begin{eqnarray}
\lefteqn{p\left(z_{n,d}=k\mid\mathbf{z_{-\left(n,d\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\beta,\gamma\right)\propto}\nonumber \\
 & \hspace{2cm}\left(n_{\left(\cdot\right),d}^{k,-\left(n,d\right)}+\alpha\beta_{k}\right)\frac{n_{w_{n,d},\left(\cdot\right)}^{k,-\left(n,d\right)}+\gamma}{\left(n_{\left(\cdot\right),\left(\cdot\right)}^{k,-\left(n,d\right)}+V\gamma\right)}\prod_{l\in\mathcal{L}_{d}}\exp\left\{ -\frac{\left(\bar{z}_{d}^{T}\eta_{l}-a_{l,d}\right)^{2}}{2}\right\} .\label{eq:z-likelihood}\end{eqnarray}
 Here, $n_{v,d}^{k,-\left(n,d^{\prime}\right)}$ represents the number
of words of type $v$ in document $d$ assigned to topic $k$ omitting
the $n^{{\rm th}}$ word of document $d^{\prime}$. The notation $(\cdot)$
in the subscript means the count resulting from summing over the omitted
subscript variable. Given Equation \ref{eq:z-likelihood}, $p\left(z_{d,n}\mid\mathbf{z_{-\left(d,n\right)}},\mathbf{a},\mathbf{w},\mathbf{\eta},\alpha,\mathbf{\beta},\gamma\right)$
can be sampled through enumeration.

\subsubsection{$p\left(\mathbf{\eta_{l}}\mid\mathbf{z},\mathbf{a},\sigma\right)$}

We now consider the conditional distribution of the regression coefficients
$\mathbf{\eta_{l}}$ for $l\in\mathcal{L}$. Given that $\mathbf{\eta_{l}}$
and $a_{l,d}$ are distributed normally, the posterior distribution
of $\mathbf{\eta_{l}}$ is normally distributed with mean $\hat{\mu}$
and covariance $\hat{\mathbf{\Sigma}}$ such that % (probably not the right place for this) We evaluated the model over various values of $\sigma$ where $\sigma=\left\{ 0.01,0.1,0.25,1,2\right\} $.
\begin{eqnarray}
\hat{\mathbf{\Sigma}}^{-1} & = & \mathbf{I}\sigma^{-1}+\bar{\mathbf{Z}}^{T}\bar{\mathbf{Z}}\\
\hat{\mu} & = & \hat{\mathbf{\Sigma}}_{i}\left(\mathbf{1}\frac{\mu}{\sigma}+\bar{\mathbf{Z}}^{T}\mathbf{a}_{l}\right).\end{eqnarray}
 This is a standard result from normal Bayesian linear regression
\citep{BishopPRML}. Here, $\bar{\mathbf{Z}}$ is a $D\times K$ matrix
such that row $d$ of $\mathbf{\bar{Z}}$ is $\bar{z}_{d}$, and $\mathbf{a}_{l}=[a_{l,1},a_{l,2},\ldots,a_{l,D}]^{T}$.
%p\left(\eta_{i_{l,c}}\mid\mathbf{z}_{1:D},\mathbf{a};\sigma\right)=\mathcal{N}\left(\eta_{i_{l,c}}\mid\hat{\mu}_{i},\hat{\Sigma}_{i}\right)\end{equation}
%\[
%\[

@@

\label{sec:experiments}

%\begin{itemize}
%\item Describe Data for both Experiments
%\item Describe the Four different conditions
%\item Describe how they are all evaluated, with and without hierarchy
%\end{itemize}
In the section we describe the application of HSLDA for prediction
in two hierarchically structured domains. Firstly, we describe using
discharge summaries to predict diagnoses, encoded as ICD-9 codes.
Discharge summaries are documents that are authored by clinicians
to summarize the course of a hospitalization. ICD-9 codes are used
mainly for billing purposes to indicate the conditions for which a
patient was treated. Secondly, we describe using Amazon.com product
descriptions to predict product categories.

\subsection{Data and Pre-Processing}

\subsubsection{Diagnosis Prediction}

@@

For each hospitalization there are usually several ICD-9 codes assigned
for billing purposes. These codes are known to be quite specific but
not very sensitive \citep{Birmetal2005}. Regardless of that fact,
this is one of the only sources for information on patient diagnoses
aside from the free text. %Aside from prediction, one of the goals is to compare the sensitivity of predictions from the HSLDA model in comparison to the codes in a case where a test closer to ground truth is available. For this we will compare whether predictions for the ICD-9 code associated with anemia are better predicted by HSLDA or by the ICD-9 codes. Anemia was chosen because hemoglobin values are readily available and the definition of anemia according the World Health Organization is approximately 12.5, with a threshold of 12 for women and 13 for men [citation].

@@

\subsubsection{Product Category Prediction}

Data for these experiments were obtained partially from the Stanford
Network Analysis Platform (SNAP) Amazon product metadata dataset \citep{SNAP}
and partially directly from the the Amazon.com website \citep{AMAZON}.
The product ID's and categorizations were obtained from the SNAP dataset
and the product descriptions were obtained directly from the website.

@@

\subsection{Comparison Models}

We applied HSLDA, along with three other closely related models, to
the clinical data and the retail product data. Specifically, we evaluate
models including sLDA with independent regressors (hierarchical constraints
on labels ignored), HSLDA fit by performing LDA followed by tree-conditional
regressions, and HSLDA fit with fixed random regression parameters.
We will refer to the three comparison models as the sLDA model, the
separate HSLDA model, and the random HSLDA model, respectively. These
models were chosen as to highlight performance in absence of hierarchical
constraints, the effect of the combined inference procedure, and regression
performance attributable solely to the hierarchical constraints.

We evaluated model performance for all three models with a range of
values for $\mu$ ($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\} )$,
the mean prior parameter for regression parameters.

\subsection{Evaluation}
%\begin{itemize}
%\item Talk about hierarchy and no hierarchy
%\item Make explicit calculation of sensitivity and 1-specificity
%\end{itemize}
For each dataset, a held out set of 1,000 documents and accompanying
labels were used for evaluation. The two main methods of evaluation
for the model are prediction and topic quality. To evaluate predictive
performance for all comparison models equivalently, each model was
evaluated with two methods. The first method augmented the observed
labels in the held out set as well as their ancestors in the hierarchy
as

@@
